Manifold Clustering in the Setting of Generalized Random Dot Product Graphs

### 2023-05-24 sdss-2023/slides.Rmd
minor updates

```{r three-curves, cache = TRUE, fig.height = 2, fig.width = 6, out.width = '100%'}
set.seed(314159)
par(mfrow = c(1, 3))

n <- 256

@@

degs <- colSums(A)
A <- A[degs > 0, degs > 0]
z <- z[degs > 0]
X <- X[degs > 0, ]
Xhat <- Xhat[degs > 0, ]

@@

qgraph::qgraph(A, 
               groups = factor(z), 
               borders = FALSE,
               legend = FALSE,
               esize = .001,
               mar = c(0, 0, 0, 0))

@@

ggplot(clust.summary.df) + 
  theme_bw() + 
  theme(text = element_text(size = 10)) + 
  scale_y_log10() +
  scale_x_log10(breaks = n.vec) +
  labs(y = 'error rate',
       x = 'n',
       colour = 'known labels per community', 
       shape = NULL) + 
  geom_line(aes(x = n, y = med.rate, colour = factor(nsamp))) + 
  geom_point(aes(x = n, y = med.rate, colour = factor(nsamp))) + 
  geom_errorbar(aes(x = n, 
                    ymin = first.q.rate, ymax = third.q.rate, 
                    colour = factor(nsamp)),
                width = .125) + 
  theme(legend.position = 'bottom') + 
  scale_colour_brewer(palette = 'Set1')
```

>>>>

```{r three-curves, cache = TRUE, fig.height = 4, fig.width = 12, out.width = '100%'}
set.seed(314159)
par(mfrow = c(1, 3))

n <- 512

@@

degs <- colSums(A)
A.trunc <- A[degs > 0, degs > 0]
z.trunc <- z[degs > 0]
# X <- X[degs > 0, ]
# Xhat <- Xhat[degs > 0, ]

@@

qgraph::qgraph(A.trunc, 
               groups = factor(z.trunc), 
               borders = FALSE,
               legend = FALSE,
               esize = .001,
               mar = c(0, 0, 0, 0))

@@

ggplot(clust.summary.df) + 
  theme_bw() + 
  theme(text = element_text(size = 10)) + 
  scale_y_log10() +
  scale_x_log10(breaks = n.vec) +
  labs(y = 'error rate',
       x = 'n',
       colour = 'known labels per community', 
       shape = NULL) + 
  geom_line(aes(x = n, y = med.rate, colour = factor(nsamp))) + 
  geom_point(aes(x = n, y = med.rate, colour = factor(nsamp))) + 
  geom_errorbar(aes(x = n, 
                    ymin = first.q.rate, ymax = third.q.rate, 
                    colour = factor(nsamp)),
                width = .05) + 
  theme(legend.position = 'bottom') + 
  scale_colour_brewer(palette = 'Set1')
```
